Notes

### 2020-02-28 Notes/Notes.tex
Added notes on how to ask MDS question

>>>>

\section{Asking MDS Question}
Instead of minimizing the size of the minimum dominating set under constraints, we can also ask if the number of nodes is smaller than an input dominating number
\begin{equation}
	\sum_{i \in V} x_i \leq \gamma_D \quad \Rightarrow \quad \sum_{i \in V} x_i - \gamma_D + s_D = 0 \, .
\end{equation}
Note that we still obtain solution vectors.
In principle this means one has to iterate approaches to get the best energy solution but it is also possible to find $E_0 = \gamma + n$ with $n\geq1$.
The QUBO now becomes
\begin{align}\label{mds2:qubo}
	Q &= 
	\begin{pmatrix}\alpha & \beta & 0 \\ 0 & \gamma & 0 \\ 0 & 0 & 0 \end{pmatrix}
	+
	A \begin{pmatrix}\alpha' & 0 & \beta' \\ 0 & 0 & 0 \\ 0 & 0 & \gamma' \end{pmatrix}
	\, , & 
	f(\vec x, \vec s, s_D)
	&=
	\vec \psi \cdot Q \cdot \vec \psi + |V| + A \gamma_D^2
	\, ,
\end{align}
where $\alpha, \beta, \gamma$ are the same as before and $\alpha', \beta', \gamma'$ implement the new constraint.
In particular 
\begin{align}
	\vec x \cdot \alpha' \vec x &= \left(\sum_i x_i\right)^2 - 2 \left(\sum_i x_i\right) \gamma_D 
	&& \Rightarrow &
	\alpha' &= \vec 1_x \vec 1_x^T - 2 \gamma_D \mathbbm{1}_x
	\\
	\vec x \cdot \beta' \vec s &= 2 \left(\sum_i x_i\right) s_D \gamma_D 
	&& \Rightarrow &
	\beta' &= 2 \gamma_D \vec 1_x B'
	\\
	\vec s \cdot \gamma' \vec s &= s_D^2 - 2 s_D \gamma_D 
	&& \Rightarrow &
	\alpha' &= B'^T B' - 2 \gamma_D B'
	\\
\end{align}
